---
title: "A excess of Cronbach's α values at rule-of-thumb cut-offs"
subtitle: "Process IO dataset"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# TODO

- NA

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(janitor)

```

# Anonymize data

```{r}

# NB this file is not publicly available due to our data sharing agreement with the metaBUS team. The processed file, saved below, simply strips DOIs.
data_bosco <- read_rds("../../data/raw/IO/alphaDb_clean_metaBUS_2018_09_09.rds") |>
  rename(doi = DOI,
         alpha = Var1RelValue)

data_processed_io <- data_bosco |>
  select(-doi)

write_rds(data_processed_io, "../../data/processed/IO/data_processed_io.rds", compress = "gz")


# remove overlap with psych dataset
data_processed_psych <- read_csv("../../data/processed/psychology/data_processed_psychology.csv") |>
  mutate(doi = str_replace(doi, "_", "/"))

data_processed_io_no_overlap_with_psych <- data_bosco |>
  anti_join(data_processed_psych, by = "doi") |>
  select(-doi)

write_rds(data_processed_io_no_overlap_with_psych, "../../data/processed/IO/data_processed_io_no_overlap_with_psych.rds", compress = "gz")

```

- N rows data_processed_io = `r nrow(data_processed_io)`
- N rows data_processed_io_no_overlap_with_psych = `r nrow(data_processed_io_no_overlap_with_psych)`
- N rows excluded based on their DOIs already appearing in the psych dataset = `r nrow(data_processed_io) - nrow(data_processed_io_no_overlap_with_psych)`
- % excluded = `r janitor::round_half_up((nrow(data_processed_io) - nrow(data_processed_io_no_overlap_with_psych))/nrow(data_processed_io)*100, 1)`%


