---
title: "Alpha curve"
subtitle: "Analyses"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# TODO

- NA

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(betareg)
library(broom)
library(extraDistr)
library(patchwork)
library(coin)

```

# Get data

```{r}

data_processed <- read_csv("../../data/processed/data_processed.csv")

data_processed_trimmed <- data_processed |>
  filter(!is.na(alpha) & 
           exclude_master == FALSE &
           regex_label != "α") # excluded as they include many estimates other than alpha values

data_processed_binned <- data_processed_trimmed %>%
  # round the alpha values to 2 decimal places, using standard rounding method
  # recode alpha values of 0 or 1 to .01 or .99, in order to be able to fit beta regression
  # nb none present in dataset
  mutate(alpha = janitor::round_half_up(alpha, 2),
         alpha = case_when(alpha == 0 ~ 0.01,
                           alpha == 1 ~ 0.99,
                           TRUE ~ alpha)) 

# dat <- data_processed_trimmed |>
#   filter(exclude_master == FALSE) |>
#   group_by(doi) |>
#   mutate(n_estimates = n()) |>
#   ungroup() |>
#   select(doi, n_estimates, exemplar, alpha, all)

```

# Descriptives

```{r}

# data_fulltexts <-
#   tibble(filename = list.files("../../data/apa_articles",
#                                pattern    = "*.txt",
#                                recursive  = TRUE,
#                                full.names = TRUE))
# 
# n_doi <- nrow(data_fulltexts)
# n_doi$n_doi
# # [1] 74470

n_doi <- 74470

paste("n articles =", 
      n_doi)


n_exclusions <- data_processed |>
  filter(exclude_master == TRUE) |>
  count(name = "n_exclusions")

paste("n exclusions =", 
      n_exclusions)


n_estimates_after_exclusions <- data_processed_trimmed |>
  count(name = "n_estimates")

paste("n alpha estimates after exclusions =", 
      n_estimates_after_exclusions)



proportion_with_valid_alpha <- 
  janitor::round_half_up(nrow(distinct(data_processed_trimmed, doi)) / n_doi, 2)

paste("proportion of articles with 1+ alpha estimates after exclusions =",
      proportion_with_valid_alpha)

```

# Kernel smoothing

## Plot

```{r}

# create tibble containing all alpha bins, for a later join
all_alphas <- tibble(alpha = as.character(seq(0.01, 0.99, 0.01)),
                     freq = 0,
                     missing = TRUE)

data_frequency_temp <- data_processed_binned %>% 
  mutate(n_total = n()) %>% 
  group_by(alpha) %>% 
  summarise(freq = sum(!is.na(alpha))/first(n_total)) %>%
  # convert alpha to character to facilitate a join later
  mutate(alpha = as.character(alpha))

# kernel density estimation
data_density <- 
  density(data_processed_binned %>%
            pull(alpha),
          n    = length(seq(0.01, 0.99, 0.01)),
          from = 0.01,
          to   = 0.99, 
          bw   = 0.03)

data_frequency <-
  # join the previous two tibbles to create a complete list of alpha bins
  data_frequency_temp %>%
  bind_rows(all_alphas %>% anti_join(data_frequency_temp, by = "alpha")) %>%
  arrange(alpha, desc(freq)) %>%
  distinct(alpha, .keep_all = TRUE) %>%
  mutate(density_kernel = data_density$y,
         missing = ifelse(is.na(missing), FALSE, missing)) %>%
  mutate(residual_kernel = freq*100 - density_kernel,
         alpha = as.numeric(alpha),
         missing = ifelse(is.na(missing), FALSE, missing))

data_diff <- data_frequency %>%
  mutate(frequency = freq*100,
         frequency_without_residual_kernel = if_else(residual_kernel > 0, frequency - residual_kernel, frequency),
         pos_resid_kernel = residual_kernel > 0,
         residual_kernel = if_else(residual_kernel > 0, residual_kernel, -1 * residual_kernel)) %>%
  dplyr::select(alpha,
                #fitted,
                density_kernel,
                pos_resid_kernel,
                frequency_without_residual_kernel,
                residual_kernel) %>%
  pivot_longer(names_to = "type",
               values_to = "residual_kernel",
               c(frequency_without_residual_kernel, residual_kernel))


color_1 <- scales::viridis_pal()(11)[3]
color_2 <- scales::viridis_pal()(11)[7]

total_n <- nrow(data_processed_trimmed)/100

p1_kernel <-
  data_diff %>%  
  mutate(type = factor(case_when(
    type == "frequency_without_residual_kernel" ~ "3",
    pos_resid_kernel ~ "2",
    TRUE ~ "1"))
  ) %>% 
  ggplot(., aes(alpha, y = residual_kernel * total_n, fill = type)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col(position = "stack") +
  geom_step(aes(y = density_kernel * total_n, group = 1), direction = "mid") +
  #ggrepel::geom_text_repel(aes(y = residual_kernel * total_n, label = if_else(type %in% c("2", "1") & alpha %in% c(0.7, 0.8, 0.9), round(residual_kernel*total_n), NA_real_)), position = "stack") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  scale_fill_manual(values = c("3" = "darkgray", "2" = color_2, "1" = color_1),
                    guide = "none") +
  scale_alpha_manual(values = c("3" = 0.35, "2" = 1, "1" = 1)) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Count")

p2_kernel <- 
  ggplot(data_frequency, aes(alpha, residual_kernel * total_n, fill = residual_kernel > 0)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col() +
  scale_fill_manual(values = c("TRUE" = color_2, "FALSE" = color_1), guide = "none") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Residual") +
  theme(legend.position = "none")

p_kernel <- p1_kernel + p2_kernel + plot_layout(nrow = 2, heights = c(0.5, 0.5))

p_kernel

ggsave("p_kernel.pdf", 
       plot = p_kernel, 
       width = 6,
       height = 4,
       units = "in")

```

## Quantify excess 

```{r}

data_inflation_kernel <- data_frequency %>%
  filter(missing == FALSE) %>%
  #filter(alpha %in% c(.69, .70, .79, .80, .89, .90)) %>%
  dplyr::select(alpha, 
                observed = freq, 
                predicted = density_kernel, 
                residual = residual_kernel) %>%
  mutate(predicted = predicted/100,
         residual = residual/100,
         inflation = (observed/predicted - 1),
         inflation_for_reporting = janitor::round_half_up(inflation*100, digits = 0),
         group = as.factor(case_when(alpha %in% c(.70, .80, .90) ~ "cutoff",
                                     TRUE ~ "non cutoff")))

#knitr::kable(data_inflation_kernel)

```

- There were `r data_inflation_kernel$inflation_for_reporting[data_inflation_kernel$alpha == 0.70]`% more observations of Cronbach's $a$ = .70 than predicted.
- There were `r data_inflation_kernel$inflation_for_reporting[data_inflation_kernel$alpha == 0.80]`% more observations of Cronbach's $a$ = .80 than predicted.
- There were `r data_inflation_kernel$inflation_for_reporting[data_inflation_kernel$alpha == 0.90]`% more observations of Cronbach's $a$ = .90 than predicted.

## Permutation test

```{r}

independence_test(residual ~ group,
                  data = data_inflation_kernel,
                  distribution = "exact",
                  alternative = "greater")

```

# Beta regression

## Plot

```{r}

# solution from https://www.andrewheiss.com/blog/2021/11/08/beta-regression-guide/#interpreting-coefficients

model_beta <- data_processed_binned %>%
  betareg(alpha ~ 1 | 1, 
          link = "logit",
          data = .)

beta_mu_intercept <- model_beta %>%
  tidy() %>%
  filter(component == "mean", term == "(Intercept)") %>%
  pull(estimate)

beta_phi_intercept <- model_beta %>%
  tidy() %>%
  filter(component == "precision", term == "(Intercept)") %>%
  pull(estimate)

data_frequency$density_beta <-
  extraDistr::dprop(x = data_frequency$alpha,
                    size = exp(beta_phi_intercept),
                    mean = plogis(beta_mu_intercept))

data_frequency <- data_frequency %>%
  mutate(residual_beta = freq*100 - density_beta,
         alpha = as.numeric(alpha),
         missing = ifelse(is.na(missing), FALSE, missing))

data_diff <- data_frequency %>%
  mutate(frequency = 100*freq,
         frequency_without_residual_beta = if_else(residual_beta > 0, frequency - residual_beta, frequency),
         pos_resid_beta = residual_beta > 0,
         residual_beta = if_else(residual_beta > 0, residual_beta, -1 * residual_beta)) %>%
  dplyr::select(alpha,
                density_beta,
                pos_resid_beta,
                frequency_without_residual_beta,
                residual_beta) %>%
  pivot_longer(names_to = "type",
               values_to = "residual_beta",
               c(frequency_without_residual_beta, residual_beta))


color_1 <- scales::viridis_pal()(11)[3]
color_2 <- scales::viridis_pal()(11)[7]

total_n <- nrow(data_processed_trimmed)/100

p1_beta <-
  data_diff %>%  
  mutate(type = factor(case_when(
    type == "frequency_without_residual_beta" ~ "3",
    pos_resid_beta ~ "2",
    TRUE ~ "1"))
  ) %>%
  ggplot(., aes(alpha, y = residual_beta * total_n, fill = type)) +
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col(position = "stack") +
  geom_step(aes(y = density_beta * total_n, group = 1), direction = "mid") +
  #ggrepel::geom_text_repel(aes(y = residual_beta * total_n, label = if_else(type %in% c("2", "1") & alpha %in% c(0.7, 0.8, 0.9), round(residual_beta*total_n), NA_real_)), position = "stack") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  scale_fill_manual(values = c("3" = "darkgray", "2" = color_2, "1" = color_1),
                    guide = "none") +
  scale_alpha_manual(values = c("3" = 0.35, "2" = 1, "1" = 1)) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Count")

p2_beta <-
  ggplot(data_frequency, aes(alpha, residual_beta * total_n, fill = residual_beta > 0)) +
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col() +
  scale_fill_manual(values = c("TRUE" = color_2, "FALSE" = color_1), guide = "none") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Residual") +
  theme(legend.position = "none")

p_beta <- p1_beta + p2_beta + plot_layout(nrow = 2, heights = c(0.5, 0.5))

p_beta

ggsave("p_beta.pdf", 
       plot = p_beta, 
       width = 6,
       height = 4,
       units = "in")

```

## Quantify excess 

```{r}

data_inflation_beta <- data_frequency %>%
  filter(missing == FALSE) %>%
  #filter(alpha %in% c(.69, .70, .79, .80, .89, .90)) %>%
  dplyr::select(alpha, 
                observed = freq, 
                predicted = density_beta, 
                residual = residual_beta) %>%
  mutate(predicted = predicted/100,
         residual = residual/100,
         inflation = (observed/predicted - 1),
         inflation_for_reporting = janitor::round_half_up(inflation*100, digits = 0),
         group = as.factor(case_when(alpha %in% c(.70, .80, .90) ~ "cutoff",
                                     TRUE ~ "non cutoff")))

#knitr::kable(data_inflation_beta)

```

- There were `r data_inflation_beta$inflation_for_reporting[data_inflation_kernel$alpha == 0.70]`% more observations of Cronbach's $a$ = .70 than predicted.
- There were `r data_inflation_beta$inflation_for_reporting[data_inflation_kernel$alpha == 0.80]`% more observations of Cronbach's $a$ = .80 than predicted.
- There were `r data_inflation_beta$inflation_for_reporting[data_inflation_kernel$alpha == 0.90]`% more observations of Cronbach's $a$ = .90 than predicted.

## Permutation test

```{r}

independence_test(residual ~ group,
                  data = data_inflation_beta,
                  distribution = "exact",
                  alternative = "greater")

```



# Taym
## Beta regression, cauchit link
```{r}

# solution from https://www.andrewheiss.com/blog/2021/11/08/beta-regression-guide/#interpreting-coefficients

model_beta <- data_processed_binned %>%
  betareg(alpha ~ 1 | 1, 
          link = "cauchit",
          data = .)

beta_mu_intercept <- model_beta %>%
  tidy() %>%
  filter(component == "mean", term == "(Intercept)") %>%
  pull(estimate)

beta_phi_intercept <- model_beta %>%
  tidy() %>%
  filter(component == "precision", term == "(Intercept)") %>%
  pull(estimate)

data_frequency$density_beta <-
  extraDistr::dprop(x = data_frequency$alpha,
                    size = exp(beta_phi_intercept),
                    mean = plogis(beta_mu_intercept))

data_frequency <- data_frequency %>%
  mutate(residual_beta = freq*100 - density_beta,
         alpha = as.numeric(alpha),
         missing = ifelse(is.na(missing), FALSE, missing))

data_diff <- data_frequency %>%
  mutate(frequency = 100*freq,
         frequency_without_residual_beta = if_else(residual_beta > 0, frequency - residual_beta, frequency),
         pos_resid_beta = residual_beta > 0,
         residual_beta = if_else(residual_beta > 0, residual_beta, -1 * residual_beta)) %>%
  dplyr::select(alpha,
                density_beta,
                pos_resid_beta,
                frequency_without_residual_beta,
                residual_beta) %>%
  pivot_longer(names_to = "type",
               values_to = "residual_beta",
               c(frequency_without_residual_beta, residual_beta))


color_1 <- scales::viridis_pal()(11)[3]
color_2 <- scales::viridis_pal()(11)[7]

total_n <- nrow(data_processed_trimmed)/100

p1_beta <-
  data_diff %>%  
  mutate(type = factor(case_when(
    type == "frequency_without_residual_beta" ~ "3",
    pos_resid_beta ~ "2",
    TRUE ~ "1"))
  ) %>%
  ggplot(., aes(alpha, y = residual_beta * total_n, fill = type)) +
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col(position = "stack") +
  geom_step(aes(y = density_beta * total_n, group = 1), direction = "mid") +
  #ggrepel::geom_text_repel(aes(y = residual_beta * total_n, label = if_else(type %in% c("2", "1") & alpha %in% c(0.7, 0.8, 0.9), round(residual_beta*total_n), NA_real_)), position = "stack") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  scale_fill_manual(values = c("3" = "darkgray", "2" = color_2, "1" = color_1),
                    guide = "none") +
  scale_alpha_manual(values = c("3" = 0.35, "2" = 1, "1" = 1)) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Count")

p2_beta <-
  ggplot(data_frequency, aes(alpha, residual_beta * total_n, fill = residual_beta > 0)) +
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col() +
  scale_fill_manual(values = c("TRUE" = color_2, "FALSE" = color_1), guide = "none") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Residual") +
  theme(legend.position = "none")

p_beta <- p1_beta + p2_beta + plot_layout(nrow = 2, heights = c(0.5, 0.5))

p_beta
```
## Some modifications to the kernel density
### Narrower bandwidth
```{r}
# create tibble containing all alpha bins, for a later join
all_alphas <- tibble(alpha = as.character(seq(0.01, 0.99, 0.01)),
                     freq = 0,
                     missing = TRUE)

data_frequency_temp <- data_processed_binned %>% 
  mutate(n_total = n()) %>% 
  group_by(alpha) %>% 
  summarise(freq = sum(!is.na(alpha))/first(n_total)) %>%
  # convert alpha to character to facilitate a join later
  mutate(alpha = as.character(alpha))

# kernel density estimation
data_density <- 
  density(data_processed_binned %>%
            pull(alpha),
          n    = length(seq(0.01, 0.99, 0.01)),
          from = 0.01,
          to   = 0.99, 
          bw   = "nrd")

data_frequency <-
  # join the previous two tibbles to create a complete list of alpha bins
  data_frequency_temp %>%
  bind_rows(all_alphas %>% anti_join(data_frequency_temp, by = "alpha")) %>%
  arrange(alpha, desc(freq)) %>%
  distinct(alpha, .keep_all = TRUE) %>%
  mutate(density_kernel = data_density$y,
         missing = ifelse(is.na(missing), FALSE, missing)) %>%
  mutate(residual_kernel = freq*100 - density_kernel,
         alpha = as.numeric(alpha),
         missing = ifelse(is.na(missing), FALSE, missing))

data_diff <- data_frequency %>%
  mutate(frequency = freq*100,
         frequency_without_residual_kernel = if_else(residual_kernel > 0, frequency - residual_kernel, frequency),
         pos_resid_kernel = residual_kernel > 0,
         residual_kernel = if_else(residual_kernel > 0, residual_kernel, -1 * residual_kernel)) %>%
  dplyr::select(alpha,
                #fitted,
                density_kernel,
                pos_resid_kernel,
                frequency_without_residual_kernel,
                residual_kernel) %>%
  pivot_longer(names_to = "type",
               values_to = "residual_kernel",
               c(frequency_without_residual_kernel, residual_kernel))


color_1 <- scales::viridis_pal()(11)[3]
color_2 <- scales::viridis_pal()(11)[7]

total_n <- nrow(data_processed_trimmed)/100

p1_kernel <-
  data_diff %>%  
  mutate(type = factor(case_when(
    type == "frequency_without_residual_kernel" ~ "3",
    pos_resid_kernel ~ "2",
    TRUE ~ "1"))
  ) %>% 
  ggplot(., aes(alpha, y = residual_kernel * total_n, fill = type)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col(position = "stack") +
  geom_step(aes(y = density_kernel * total_n, group = 1), direction = "mid") +
  #ggrepel::geom_text_repel(aes(y = residual_kernel * total_n, label = if_else(type %in% c("2", "1") & alpha %in% c(0.7, 0.8, 0.9), round(residual_kernel*total_n), NA_real_)), position = "stack") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  scale_fill_manual(values = c("3" = "darkgray", "2" = color_2, "1" = color_1),
                    guide = "none") +
  scale_alpha_manual(values = c("3" = 0.35, "2" = 1, "1" = 1)) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Count")

p2_kernel <- 
  ggplot(data_frequency, aes(alpha, residual_kernel * total_n, fill = residual_kernel > 0)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col() +
  scale_fill_manual(values = c("TRUE" = color_2, "FALSE" = color_1), guide = "none") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Residual") +
  theme(legend.position = "none")

p_kernel <- p1_kernel + p2_kernel + plot_layout(nrow = 2, heights = c(0.5, 0.5))

p_kernel
```

### Change distribution
```{r}
# create tibble containing all alpha bins, for a later join
all_alphas <- tibble(alpha = as.character(seq(0.01, 0.99, 0.01)),
                     freq = 0,
                     missing = TRUE)

data_frequency_temp <- data_processed_binned %>% 
  mutate(n_total = n()) %>% 
  group_by(alpha) %>% 
  summarise(freq = sum(!is.na(alpha))/first(n_total)) %>%
  # convert alpha to character to facilitate a join later
  mutate(alpha = as.character(alpha))

# kernel density estimation
data_density <- 
  density(data_processed_binned %>%
            pull(alpha),
          n    = length(seq(0.01, 0.99, 0.01)),
          from = 0.01,
          to   = 0.99, 
          bw   = 0.03,
          kernel = "rectangular")

data_frequency <-
  # join the previous two tibbles to create a complete list of alpha bins
  data_frequency_temp %>%
  bind_rows(all_alphas %>% anti_join(data_frequency_temp, by = "alpha")) %>%
  arrange(alpha, desc(freq)) %>%
  distinct(alpha, .keep_all = TRUE) %>%
  mutate(density_kernel = data_density$y,
         missing = ifelse(is.na(missing), FALSE, missing)) %>%
  mutate(residual_kernel = freq*100 - density_kernel,
         alpha = as.numeric(alpha),
         missing = ifelse(is.na(missing), FALSE, missing))

data_diff <- data_frequency %>%
  mutate(frequency = freq*100,
         frequency_without_residual_kernel = if_else(residual_kernel > 0, frequency - residual_kernel, frequency),
         pos_resid_kernel = residual_kernel > 0,
         residual_kernel = if_else(residual_kernel > 0, residual_kernel, -1 * residual_kernel)) %>%
  dplyr::select(alpha,
                #fitted,
                density_kernel,
                pos_resid_kernel,
                frequency_without_residual_kernel,
                residual_kernel) %>%
  pivot_longer(names_to = "type",
               values_to = "residual_kernel",
               c(frequency_without_residual_kernel, residual_kernel))


color_1 <- scales::viridis_pal()(11)[3]
color_2 <- scales::viridis_pal()(11)[7]

total_n <- nrow(data_processed_trimmed)/100

p1_kernel <-
  data_diff %>%  
  mutate(type = factor(case_when(
    type == "frequency_without_residual_kernel" ~ "3",
    pos_resid_kernel ~ "2",
    TRUE ~ "1"))
  ) %>% 
  ggplot(., aes(alpha, y = residual_kernel * total_n, fill = type)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col(position = "stack") +
  geom_step(aes(y = density_kernel * total_n, group = 1), direction = "mid") +
  #ggrepel::geom_text_repel(aes(y = residual_kernel * total_n, label = if_else(type %in% c("2", "1") & alpha %in% c(0.7, 0.8, 0.9), round(residual_kernel*total_n), NA_real_)), position = "stack") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  scale_fill_manual(values = c("3" = "darkgray", "2" = color_2, "1" = color_1),
                    guide = "none") +
  scale_alpha_manual(values = c("3" = 0.35, "2" = 1, "1" = 1)) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Count")

p2_kernel <- 
  ggplot(data_frequency, aes(alpha, residual_kernel * total_n, fill = residual_kernel > 0)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col() +
  scale_fill_manual(values = c("TRUE" = color_2, "FALSE" = color_1), guide = "none") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Residual") +
  theme(legend.position = "none")

p_kernel <- p1_kernel + p2_kernel + plot_layout(nrow = 2, heights = c(0.5, 0.5))

p_kernel
```




## Bayesian Beta reg
```{r}
library(brms)
library(tidybayes)

bayes_beta <- data_processed_binned %>%
  brm(
  bf(alpha ~ 1,
     phi ~ 1),
  data = .,
  family = Beta(),
  chains = 4, iter= 2000, warmup = 1000,
  cores = 4, seed = 914914
)
pp_check(bayes_beta)
summary(bayes_beta)
browseURL('https://www.youtube.com/watch?v=dJ9FY06urr4&ab_channel=ceilingsoldier')
```

`



# Session info

```{r}

sessionInfo()

```
