---
title: "A excess of Cronbach's α values at rule-of-thumb cut-offs"
subtitle: "Analyses of I/O dataset"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# TODO

- Add descriptives

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)

```

# Dependencies

```{r}

library(tidyverse)
library(broom)
library(extraDistr)
library(patchwork)
library(coin)

dir.create("plots")

```

# Get data

```{r}

data_processed <- read_rds("../../data/processed/IO/data_processed_io.rds")

data_processed_binned <- data_processed %>%
  # round the alpha values to 2 decimal places, using standard rounding method
  # recode alpha values of 0 or 1 to .01 or .99, in order to be able to fit beta regression
  # nb none present in dataset
  mutate(alpha = janitor::round_half_up(alpha, 2),
         alpha = case_when(alpha == 0 ~ 0.01,
                           alpha == 1 ~ 0.99,
                           TRUE ~ alpha)) 

```

# Kernel smoothing - by use of construct

## Data subsetting

```{r}

p_freq <- 
  data_processed_binned |>
  count(Var1) |>
  count(n) |>
  ggplot(aes(n, nn * 10)) +
  geom_col(color = "black", width = 0.01) + 
  scale_y_log10(labels = function(y) y/10) +
  theme_classic() +
  ylab("Count (constructs)") +
  xlab("Count (alpha estimates associated with that construct)") 

p_freq

ggsave("plots/p_frequency_of_construct_use_IO.pdf",
       plot = p_freq,
       width = 6,
       height = 4,
       units = "in")


p_freq_log10 <- 
  data_processed_binned |>
  count(Var1) |>
  count(n) |>
  ggplot(aes(n, nn * 10)) +
  geom_col(color = "black", width = 0.01) + 
  scale_y_log10(labels = function(y) y/10) +
  scale_x_log10() +
  theme_classic() +
  ylab("Count (constructs)") +
  xlab("Count (alpha estimates associated with that construct)") 

p_freq_log10

ggsave("plots/p_frequency_of_construct_use_log10_IO.pdf",
       plot = p_freq_log10,
       width = 6,
       height = 4,
       units = "in")



constructs_used_once <- data_processed_binned |>
  count(Var1) |>
  filter(n == 1)

data_processed_binned_constructs_used_once <- data_processed_binned |>
  semi_join(constructs_used_once, by = "Var1")

data_processed_binned_constructs_used_many_times <- data_processed_binned |>
  anti_join(constructs_used_once, by = "Var1")


constructs_used_100 <- data_processed_binned |>
  count(Var1) |>
  filter(n >= 100)

data_processed_binned_constructs_used_100 <- data_processed_binned |>
  semi_join(constructs_used_100, by = "Var1")

rm(data_processed_binned,
   data_processed)

```

## Constructs used once

### Model and plot

```{r}

# create tibble containing all alpha bins, for a later join
all_alphas <- tibble(alpha = as.character(seq(0.01, 0.99, 0.01)),
                     freq = 0,
                     missing = TRUE)

data_frequency_temp <- data_processed_binned_constructs_used_once %>% 
  mutate(n_total = n()) %>% 
  group_by(alpha) %>% 
  summarise(freq = sum(!is.na(alpha))/first(n_total)) %>%
  # convert alpha to character to facilitate a join later
  mutate(alpha = as.character(alpha))

# kernel density estimation
data_density <- 
  density(data_processed_binned_constructs_used_once %>%
            pull(alpha),
          n      = length(seq(0.01, 0.99, 0.01)),
          from   = 0.01,
          to     = 0.99, 
          kernel = "gaussian",
          bw     = 0.01) # "nrd0" in the psychology dataset returns 0.01

data_frequency <-
  # join the previous two tibbles to create a complete list of alpha bins
  data_frequency_temp %>%
  bind_rows(all_alphas %>% anti_join(data_frequency_temp, by = "alpha")) %>%
  arrange(alpha, desc(freq)) %>%
  distinct(alpha, .keep_all = TRUE) %>%
  mutate(density_kernel = data_density$y,
         missing = ifelse(is.na(missing), FALSE, missing)) %>%
  mutate(residual_kernel = freq*100 - density_kernel,
         alpha = as.numeric(alpha),
         missing = ifelse(is.na(missing), FALSE, missing))

data_diff <- data_frequency %>%
  mutate(frequency = freq*100,
         frequency_without_residual_kernel = if_else(residual_kernel > 0, frequency - residual_kernel, frequency),
         pos_resid_kernel = residual_kernel > 0,
         residual_kernel = if_else(residual_kernel > 0, residual_kernel, -1 * residual_kernel)) %>%
  dplyr::select(alpha,
                #fitted,
                density_kernel,
                pos_resid_kernel,
                frequency_without_residual_kernel,
                residual_kernel) %>%
  pivot_longer(names_to = "type",
               values_to = "residual_kernel",
               c(frequency_without_residual_kernel, residual_kernel))


color_1 <- scales::viridis_pal()(11)[3]
color_2 <- scales::viridis_pal()(11)[7]

total_n <- nrow(data_processed_binned_constructs_used_once)/100

p1_kernel <-
  data_diff %>%  
  mutate(type = factor(case_when(
    type == "frequency_without_residual_kernel" ~ "3",
    pos_resid_kernel ~ "2",
    TRUE ~ "1"))
  ) %>% 
  ggplot(., aes(alpha, y = residual_kernel * total_n, fill = type)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col(position = "stack") +
  geom_step(aes(y = density_kernel * total_n, group = 1), direction = "mid") +
  #ggrepel::geom_text_repel(aes(y = residual_kernel * total_n, label = if_else(type %in% c("2", "1") & alpha %in% c(0.7, 0.8, 0.9), round(residual_kernel*total_n), NA_real_)), position = "stack") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  scale_fill_manual(values = c("3" = "darkgray", "2" = color_2, "1" = color_1),
                    guide = "none") +
  scale_alpha_manual(values = c("3" = 0.35, "2" = 1, "1" = 1)) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Count") +
  ylim(0, 1800)

p2_kernel <- 
  ggplot(data_frequency, aes(alpha, residual_kernel * total_n, fill = residual_kernel > 0)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col() +
  scale_fill_manual(values = c("TRUE" = color_2, "FALSE" = color_1), guide = "none") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Residual") +
  theme(legend.position = "none")

p_kernel <- p1_kernel + p2_kernel + plot_layout(nrow = 2, heights = c(0.5, 0.5))

p_kernel

# ggsave("plots/p_kernel_IO.pdf", 
#        plot = p_kernel, 
#        width = 6,
#        height = 4,
#        units = "in")

```

### Quantify excess 

```{r}

data_inflation_kernel <- data_frequency %>%
  filter(missing == FALSE) %>%
  dplyr::select(alpha, 
                observed = freq, 
                predicted = density_kernel, 
                residual = residual_kernel) %>%
  mutate(predicted = predicted/100,
         residual = residual/100,
         inflation = (observed/predicted - 1),
         inflation_for_reporting = janitor::round_half_up(inflation*100, digits = 0),
         group_3_cutoffs = as.factor(case_when(alpha %in% c(.70, .80, .90) ~ "cutoff",
                                               TRUE ~ "non cutoff")),
         group_1_cutoff = as.factor(case_when(alpha %in% c(.70) ~ "cutoff",
                                               TRUE ~ "non cutoff")))

```

- There were `r data_inflation_kernel$inflation_for_reporting[data_inflation_kernel$alpha == 0.70]`% more observations of Cronbach's $\alpha$ = .70 than predicted.

### Permutation test

.70 against the rest:

```{r}

independence_test(residual ~ group_1_cutoff,
                  data = data_inflation_kernel,
                  distribution = "exact",
                  alternative = "greater")

```

## Constructs used more than once 

### Model and plot

```{r}

# create tibble containing all alpha bins, for a later join
all_alphas <- tibble(alpha = as.character(seq(0.01, 0.99, 0.01)),
                     freq = 0,
                     missing = TRUE)

data_frequency_temp <- data_processed_binned_constructs_used_many_times %>% 
  mutate(n_total = n()) %>% 
  group_by(alpha) %>% 
  summarise(freq = sum(!is.na(alpha))/first(n_total)) %>%
  # convert alpha to character to facilitate a join later
  mutate(alpha = as.character(alpha))

# kernel density estimation
data_density <- 
  density(data_processed_binned_constructs_used_many_times %>%
            pull(alpha),
          n      = length(seq(0.01, 0.99, 0.01)),
          from   = 0.01,
          to     = 0.99, 
          kernel = "gaussian",
          bw     = 0.01) # "nrd0" in the psychology dataset returns 0.01

data_frequency <-
  # join the previous two tibbles to create a complete list of alpha bins
  data_frequency_temp %>%
  bind_rows(all_alphas %>% anti_join(data_frequency_temp, by = "alpha")) %>%
  arrange(alpha, desc(freq)) %>%
  distinct(alpha, .keep_all = TRUE) %>%
  mutate(density_kernel = data_density$y,
         missing = ifelse(is.na(missing), FALSE, missing)) %>%
  mutate(residual_kernel = freq*100 - density_kernel,
         alpha = as.numeric(alpha),
         missing = ifelse(is.na(missing), FALSE, missing))

data_diff <- data_frequency %>%
  mutate(frequency = freq*100,
         frequency_without_residual_kernel = if_else(residual_kernel > 0, frequency - residual_kernel, frequency),
         pos_resid_kernel = residual_kernel > 0,
         residual_kernel = if_else(residual_kernel > 0, residual_kernel, -1 * residual_kernel)) %>%
  dplyr::select(alpha,
                #fitted,
                density_kernel,
                pos_resid_kernel,
                frequency_without_residual_kernel,
                residual_kernel) %>%
  pivot_longer(names_to = "type",
               values_to = "residual_kernel",
               c(frequency_without_residual_kernel, residual_kernel))


color_1 <- scales::viridis_pal()(11)[3]
color_2 <- scales::viridis_pal()(11)[7]

total_n <- nrow(data_processed_binned_constructs_used_many_times)/100

p1_kernel <-
  data_diff %>%  
  mutate(type = factor(case_when(
    type == "frequency_without_residual_kernel" ~ "3",
    pos_resid_kernel ~ "2",
    TRUE ~ "1"))
  ) %>% 
  ggplot(., aes(alpha, y = residual_kernel * total_n, fill = type)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col(position = "stack") +
  geom_step(aes(y = density_kernel * total_n, group = 1), direction = "mid") +
  #ggrepel::geom_text_repel(aes(y = residual_kernel * total_n, label = if_else(type %in% c("2", "1") & alpha %in% c(0.7, 0.8, 0.9), round(residual_kernel*total_n), NA_real_)), position = "stack") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  scale_fill_manual(values = c("3" = "darkgray", "2" = color_2, "1" = color_1),
                    guide = "none") +
  scale_alpha_manual(values = c("3" = 0.35, "2" = 1, "1" = 1)) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Count") +
  ylim(0, 3000)

p2_kernel <- 
  ggplot(data_frequency, aes(alpha, residual_kernel * total_n, fill = residual_kernel > 0)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col() +
  scale_fill_manual(values = c("TRUE" = color_2, "FALSE" = color_1), guide = "none") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Residual") +
  theme(legend.position = "none")

p_kernel <- p1_kernel + p2_kernel + plot_layout(nrow = 2, heights = c(0.5, 0.5))

p_kernel

# ggsave("plots/p_kernel_IO.pdf", 
#        plot = p_kernel, 
#        width = 6,
#        height = 4,
#        units = "in")

```

### Quantify excess 

```{r}

data_inflation_kernel <- data_frequency %>%
  filter(missing == FALSE) %>%
  dplyr::select(alpha, 
                observed = freq, 
                predicted = density_kernel, 
                residual = residual_kernel) %>%
  mutate(predicted = predicted/100,
         residual = residual/100,
         inflation = (observed/predicted - 1),
         inflation_for_reporting = janitor::round_half_up(inflation*100, digits = 0),
         group_3_cutoffs = as.factor(case_when(alpha %in% c(.70, .80, .90) ~ "cutoff",
                                               TRUE ~ "non cutoff")),
         group_1_cutoff = as.factor(case_when(alpha %in% c(.70) ~ "cutoff",
                                               TRUE ~ "non cutoff")))

```

- There were `r data_inflation_kernel$inflation_for_reporting[data_inflation_kernel$alpha == 0.70]`% more observations of Cronbach's $\alpha$ = .70 than predicted.

### Permutation test

.70 against the rest:

```{r}

independence_test(residual ~ group_1_cutoff,
                  data = data_inflation_kernel,
                  distribution = "exact",
                  alternative = "greater")

```

## Constructs used 100 times or more  

### Model and plot

```{r}

# create tibble containing all alpha bins, for a later join
all_alphas <- tibble(alpha = as.character(seq(0.01, 0.99, 0.01)),
                     freq = 0,
                     missing = TRUE)

data_frequency_temp <- data_processed_binned_constructs_used_100 %>% 
  mutate(n_total = n()) %>% 
  group_by(alpha) %>% 
  summarise(freq = sum(!is.na(alpha))/first(n_total)) %>%
  # convert alpha to character to facilitate a join later
  mutate(alpha = as.character(alpha))

# kernel density estimation
data_density <- 
  density(data_processed_binned_constructs_used_100 %>%
            pull(alpha),
          n      = length(seq(0.01, 0.99, 0.01)),
          from   = 0.01,
          to     = 0.99, 
          kernel = "gaussian",
          bw     = 0.01) # "nrd0" in the psychology dataset returns 0.01

data_frequency <-
  # join the previous two tibbles to create a complete list of alpha bins
  data_frequency_temp %>%
  bind_rows(all_alphas %>% anti_join(data_frequency_temp, by = "alpha")) %>%
  arrange(alpha, desc(freq)) %>%
  distinct(alpha, .keep_all = TRUE) %>%
  mutate(density_kernel = data_density$y,
         missing = ifelse(is.na(missing), FALSE, missing)) %>%
  mutate(residual_kernel = freq*100 - density_kernel,
         alpha = as.numeric(alpha),
         missing = ifelse(is.na(missing), FALSE, missing))

data_diff <- data_frequency %>%
  mutate(frequency = freq*100,
         frequency_without_residual_kernel = if_else(residual_kernel > 0, frequency - residual_kernel, frequency),
         pos_resid_kernel = residual_kernel > 0,
         residual_kernel = if_else(residual_kernel > 0, residual_kernel, -1 * residual_kernel)) %>%
  dplyr::select(alpha,
                #fitted,
                density_kernel,
                pos_resid_kernel,
                frequency_without_residual_kernel,
                residual_kernel) %>%
  pivot_longer(names_to = "type",
               values_to = "residual_kernel",
               c(frequency_without_residual_kernel, residual_kernel))


color_1 <- scales::viridis_pal()(11)[3]
color_2 <- scales::viridis_pal()(11)[7]

total_n <- nrow(data_processed_binned_constructs_used_100)/100

p1_kernel <-
  data_diff %>%  
  mutate(type = factor(case_when(
    type == "frequency_without_residual_kernel" ~ "3",
    pos_resid_kernel ~ "2",
    TRUE ~ "1"))
  ) %>% 
  ggplot(., aes(alpha, y = residual_kernel * total_n, fill = type)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col(position = "stack") +
  geom_step(aes(y = density_kernel * total_n, group = 1), direction = "mid") +
  #ggrepel::geom_text_repel(aes(y = residual_kernel * total_n, label = if_else(type %in% c("2", "1") & alpha %in% c(0.7, 0.8, 0.9), round(residual_kernel*total_n), NA_real_)), position = "stack") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  scale_fill_manual(values = c("3" = "darkgray", "2" = color_2, "1" = color_1),
                    guide = "none") +
  scale_alpha_manual(values = c("3" = 0.35, "2" = 1, "1" = 1)) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Count") +
  ylim(0, 600)

p2_kernel <- 
  ggplot(data_frequency, aes(alpha, residual_kernel * total_n, fill = residual_kernel > 0)) + 
  geom_vline(xintercept = c(0.7, 0.8, 0.9), linetype = "dotted") +
  geom_col() +
  scale_fill_manual(values = c("TRUE" = color_2, "FALSE" = color_1), guide = "none") +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.1),
                     labels = seq(from = 0, to = 1, by = 0.1),
                     minor_breaks = NULL) +
  theme_bw() +
  labs(x = expression("Cronbach's" ~ alpha),
       y = "Residual") +
  theme(legend.position = "none")

p_kernel <- p1_kernel + p2_kernel + plot_layout(nrow = 2, heights = c(0.5, 0.5))

p_kernel

# ggsave("plots/p_kernel_IO.pdf", 
#        plot = p_kernel, 
#        width = 6,
#        height = 4,
#        units = "in")

```

### Quantify excess 

```{r}

data_inflation_kernel <- data_frequency %>%
  filter(missing == FALSE) %>%
  dplyr::select(alpha, 
                observed = freq, 
                predicted = density_kernel, 
                residual = residual_kernel) %>%
  mutate(predicted = predicted/100,
         residual = residual/100,
         inflation = (observed/predicted - 1),
         inflation_for_reporting = janitor::round_half_up(inflation*100, digits = 0),
         group_3_cutoffs = as.factor(case_when(alpha %in% c(.70, .80, .90) ~ "cutoff",
                                               TRUE ~ "non cutoff")),
         group_1_cutoff = as.factor(case_when(alpha %in% c(.70) ~ "cutoff",
                                               TRUE ~ "non cutoff")))

```

- There were `r data_inflation_kernel$inflation_for_reporting[data_inflation_kernel$alpha == 0.70]`% more observations of Cronbach's $\alpha$ = .70 than predicted.

### Permutation test

.70 against the rest:

```{r}

independence_test(residual ~ group_1_cutoff,
                  data = data_inflation_kernel,
                  distribution = "exact",
                  alternative = "greater")

```

# Session info

```{r}

sessionInfo()

```
